\begingroup
\footnotesize
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}

\begin{thebibliography}{99}

\bibitem{ref1}
Liu, C., \& Wang, J. (2021, February 28). \textit{Parallel implementations of random time algorithm for chemical network stochastic simulations}. arXiv.org. \url{https://arxiv.org/abs/2103.00405}

\bibitem{ref2}
Zhou, X., \& Zafarani, R. (2020). A survey of fake news. \textit{ACM Computing Surveys, 53}(5), 1--40. \url{https://doi.org/10.1145/3395046}

\bibitem{ref3}
Zhao, W., Zhu, X., He, Z., Zhang, X., \& Lei, Z. (2023). Cross-Architecture Distillation for Face Recognition. In \textit{Proceedings of the 31st ACM International Conference on Multimedia} (pp. 8076--8085). \url{https://doi.org/10.1145/3581783.3611711}

\bibitem{ref4}
IEEE transactions on neural networks and learning Systems. (2026, January 7). Grokipedia. \url{https://grokipedia.com/page/ieee_transactions_on_neural_networks_and_learning_systems}

\bibitem{ref5}
Guo, T., Li, X., Yang, H., Liang, X., Yuan, Y., Hou, J., Ke, B., Zhang, C., He, J., Zhang, S., Yu, E., \& Ou, W. (2023). Query-dominant User Interest Network for Large-Scale Search Ranking. In \textit{Proceedings of the 32nd ACM International Conference on Information and Knowledge Management} (pp. 629--638). \url{https://doi.org/10.1145/3583780.3615022}

\bibitem{ref6}
Liu, Y., Ott, M., Goyal, N., Du, J., Joshi, M., Chen, D., Levy, O., Lewis, M., Zettlemoyer, L., \& Stoyanov, V. (2019, July 26). ROBERTA: A robustly optimized BERT pretraining approach. arXiv.org. \url{https://arxiv.org/abs/1907.11692}

\bibitem{ref7}
Radford, A., Kim, J. W., Hallacy, C., Ramesh, A., Goh, G., Agarwal, S., Sastry, G., Askell, A., Mishkin, P., Clark, J., Krueger, G., \& Sutskever, I. (2021, February 26). Learning transferable visual models from natural language supervision. arXiv.org. \url{https://arxiv.org/abs/2103.00020}

\bibitem{ref8}
Vaswani, A., Shazeer, N., Google Brain, Parmar, N., Uszkoreit, J., Jones, L., Gomez, A. N., University of Toronto, Kaiser, \L{}., Google Research, \& Polosukhin, I. (2017). Attention is all you need [Conference-proceeding]. \url{https://proceedings.neurips.cc/paper_files/paper/2017/file/3f5ee243547dee91fbd053c1c4a845aa-Paper.pdf}

\bibitem{ref9}
He, K., Zhang, X., Ren, S., \& Sun, J. (2016). Deep residual learning for image recognition. In \textit{Proceedings of the IEEE conference on computer vision and pattern recognition} (pp. 770-778). \url{https://doi.org/10.1109/CVPR.2016.90}

\bibitem{ref10}
Guo, C., Pleiss, G., Sun, Y., \& Weinberger, K. Q. (2017, July 17). On calibration of modern neural networks. PMLR. \url{https://proceedings.mlr.press/v70/guo17a.htm}

\bibitem{ref11}
Comito, C., Caroprese, L., \& Zumpano, E. (2023). Multimodal fake news detection on social media: a survey of deep learning techniques. \textit{Social Network Analysis and Mining, 13}(1). \url{https://doi.org/10.1007/s13278-023-01104-w}

\bibitem{ref12}
Devlin, J., Chang, M. W., Lee, K., \& Toutanova, K. (2019). BERT: Pre-training of deep bidirectional transformers for language understanding. In \textit{Proceedings of the 2019 Conference of the North American Chapter of the Association for Computational Linguistics: Human Language Technologies, Volume 1 (Long and Short Papers)} (pp. 4171-4186). \url{https://aclanthology.org/N19-1423}

\bibitem{ref13}
Nam, H., Ha, J., \& Kim, J. (2016, November 2). Dual attention networks for multimodal reasoning and matching. arXiv.org. \url{https://arxiv.org/abs/1611.00471}

\bibitem{ref14}
Chen, W., Liu, Y., Binglin Chen, Jiangdon Su, Yongsen Zheng, \& Liang Lin. (2021). Cross-modal Causal Relation Alignment for Video Question Grounding. In \textit{IEEE/CVF Conference on Computer Vision and Pattern Recognition}. \url{https://openaccess.thecvf.com/content/CVPR2025/papers/Chen_Cross-modal_Causal_Relation_Alignment_for_Video_Question_Grounding_CVPR_2025_paper.pdf}

\bibitem{ref15}
Wang, H., Zhang, F., Xie, X., \& Guo, M. (2018, January 25). DKN: Deep Knowledge-Aware Network for news recommendation. arXiv.org. \url{https://arxiv.org/abs/1801.08284}

\bibitem{ref16}
Xing, Y., Zhai, C., Che, Z., Pan, H., Li, K., Zhang, B., Yao, Z., \& Si, X. (2025). A multimodal fake news detection model based on bidirectional semantic enhancement and adversarial network under Web3.0. \textit{Electronics, 14}(18), 3652. \url{https://doi.org/10.3390/electronics14183652}

\bibitem{ref17}
Guo, Z., Liu, H., Zuo, L., \& Wen, J. (2025). Bilinear learning with dual-chain feature attention for multimodal rumor detection. \textit{Mathematics, 13}(11), 1731. \url{https://doi.org/10.3390/math13111731}

\bibitem{ref18}
Vrande\v{c}i\'{c}, D., \& Kr\"{o}tzsch, M. (2014). Wikidata. \textit{Communications of the ACM, 57}(10), 78--85. \url{https://doi.org/10.1145/2629489}

\bibitem{ref19}
Bordes, A., Garcia-Duran, A., Weston, J., \& Yakhnenko, O. (2013). Translating embeddings for modeling multi-relational data. \url{https://papers.nips.cc/paper_files/paper/2013/hash/1cecc7a77928ca8133fa24680a88d2f9-Abstract.html}

\bibitem{ref20}
Kipf, T. N., \& Welling, M. (2016, September 9). Semi-Supervised Classification with Graph Convolutional Networks. arXiv.org. \url{https://arxiv.org/abs/1609.02907}

\bibitem{ref21}
Veli\v{c}kovi\'{c}, P., Cucurull, G., Casanova, A., Romero, A., Li\`{o}, P., \& Bengio, Y. (2017, October 30). Graph attention networks. arXiv.org. \url{https://arxiv.org/abs/1710.10903}

\bibitem{ref22}
Schroff, F., Kalenichenko, D., \& Philbin, J. (2015). FaceNet: A unified embedding for face recognition and clustering. In \textit{Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition (CVPR)} (pp. 815-823). \url{https://doi.org/10.1109/CVPR.2015.7298682}

\bibitem{ref23}
Chen, T., Kornblith, S., Norouzi, M., \& Hinton, G. (2020, February 13). A simple framework for contrastive learning of visual representations. arXiv.org. \url{https://arxiv.org/abs/2002.05709}

\bibitem{ref24}
He, Z., Wang, H., \& Li, L. (2025). Fake news detection based on contrastive learning and cross-modal interaction. \textit{Symmetry, 17}(8), 1260. \url{https://doi.org/10.3390/sym17081260}

\bibitem{ref25}
Yang, Y., Shi, X., Li, H., Fan, B., \& Xu, Y. (2025). Fake news detection in short videos by integrating semantic credibility and multi-granularity contrastive learning. \textit{Applied Sciences, 15}(23), 12621. \url{https://doi.org/10.3390/app152312621}

\bibitem{ref26}
Wu, B., Hu, R., Wang, J., Sui, X., Sun, J., Liu, J., \& Qu, Y. (2026). A multimodal fake news detection method based on contrastive learning and variational autoencoder. \textit{Mathematics, 14}(10), 1773. \url{https://doi.org/10.3390/math14101773}

\bibitem{ref27}
Li, J., Li, D., Xiong, C., \& Hoi, S. (2022, January 28). BLIP: Bootstrapping Language-Image Pre-training for Unified Vision-Language Understanding and Generation. arXiv.org. \url{https://arxiv.org/abs/2201.12086}

\bibitem{ref28}
Dosovitskiy, A., Beyer, L., Kolesnikov, A., Weissenborn, D., Zhai, X., Unterthiner, T., Dehghani, M., Minderer, M., Heigold, G., Gelly, S., Uszkoreit, J., \& Houlsby, N. (2020, October 22). An Image is Worth 16x16 Words: Transformers for Image Recognition at Scale. arXiv.org. \url{https://arxiv.org/abs/2010.11929}

\bibitem{ref29}
Houlsby, N., Giurgiu, A., Jastrzebski, S., Morrone, B., Quentin, D. L., Gesmundo, A., Attariyan, M., \& Gelly, S. (2019b, February 2). Parameter-Efficient Transfer Learning for NLP. arXiv.org. \url{https://arxiv.org/abs/1902.00751}

\bibitem{ref30}
Pakdaman Naeini, M., Cooper, G. F., Hauskrecht, M., Intelligent Systems Program, University of Pittsburgh, PA, USA, Department of Biomedical Informatics, University of Pittsburgh, PA, USA, \& Computer Science Department, University of Pittsburgh, PA, USA. (2015). Obtaining Well Calibrated Probabilities Using Bayesian Binning. In \textit{Proceedings of the AAAI Conference on Artificial Intelligence}. \url{https://www.dbmi.pitt.edu/wp-content/uploads/2022/10/Obtaining-well-calibrated-probabilities-using-Bayesian-binning.pdf}

\bibitem{ref31}
Brier G. W. (n.d.). VERIFICATION OF FORECASTS EXPRESSED IN TERMS OF PROBABILITY \url{https://scholarhub.vn/publication/VERIFICATION-OF-FORECASTS-EXPRESSED-IN-TERMS-OF-PROBABILITY/44e9e4ca-23c5-4987-9569-74e2de3b538c}

\bibitem{ref32}
Sokolova, M., \& Lapalme, G. (2009). A systematic analysis of performance measures for classification tasks. \textit{Information Processing \& Management, 45}(4), 427-437. \url{https://doi.org/10.1016/j.ipm.2009.03.002}

\bibitem{ref33}
Liu, P., Qian, W., Xu, D., Ren, B., \& Cao, J. (2023). Multi-modal fake news detection via bridging the gap between modals. \textit{Entropy, 25}(4), 614. \url{https://doi.org/10.3390/e25040614}

\bibitem{ref34}
Ding, H., Lou, S., Ye, H., \& Chen, Y. (2025). MT-CMVAD: A multi-modal transformer framework for cross-modal video anomaly detection. \textit{Applied Sciences, 15}(12), 6773. \url{https://doi.org/10.3390/app15126773}

\bibitem{ref35}
Chen, W., Liu, Y., Binglin Chen, Jiangdon Su, Yongsen Zheng, \& Liang Lin. (2021b). Cross-modal Causal Relation Alignment for Video Question Grounding. In \textit{Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR 2025)}. \url{https://openaccess.thecvf.com/content/CVPR2025/papers/Chen_Cross-modal_Causal_Relation_Alignment_for_Video_Question_Grounding_CVPR_2025_paper.pdf}

\bibitem{ref36}
Lan, X., Zhang, S., Bai, Y., \& Qin, X. (2025). Fine-grained multispectral fusion for oriented object detection in remote sensing. \textit{Remote Sensing, 17}(22), 3769. \url{https://doi.org/10.3390/rs17223769}

\bibitem{ref37}
Chen, W., Liu, Y., Wang, C., Zhu, J., Li, G., Liu, C.-L., \& Lin, L. (2025). Cross-Modal causal representation learning for radiology report generation. In \textit{IEEE TRANSACTIONS ON IMAGE PROCESSING} (Vol. 34) [Journal-article]. \url{https://doi.org/10.1109/TIP.2025.3568746}

\bibitem{ref38}
FineFake: a Knowledge-Enriched dataset for Fine-Grained Multi-Domain fake news detection. (n.d.). \url{https://arxiv.org/html/2404.01336v1#S3}

\bibitem{ref39}
Learning Transferable Visual Models From Natural Language Supervision. (n.d.). In \textit{International Conference on Machine Learning 2021}. \url{https://proceedings.mlr.press/v139/radford21a/radford21a.pdf}

\bibitem{ref40}
Buda, M., Maki, A., \& Mazurowski, M. A. (2018). A systematic study of the class imbalance problem in convolutional neural networks. \textit{Neural Networks, 106}, 249-259. \url{https://doi.org/10.1016/j.neunet.2018.07.011}

\bibitem{ref41}
Efron, B. (1979). Bootstrap methods: Another look at the jackknife. \textit{The Annals of Statistics, 7}(1), 1--26. \url{https://sites.stat.washington.edu/courses/stat527/s14/readings/ann_stat1979.pdf}

\bibitem{ref42}
Tan, R., Plummer, B. A., Saenko, K., Boston University, \& MIT-IBM Watson AI Lab. (n.d.). Detecting Cross-Modal inconsistency to defend against neural fake news. In \textit{Proceedings of the 2020 Conference on Empirical Methods in Natural Language Processing} (pp. 2081--2106) [Conference-proceeding]. Association for Computational Linguistics. \url{https://aclanthology.org/2020.emnlp-main.163.pdf}

\bibitem{ref43}
Shen, X., Huang, M., Hu, Z., Cai, S., \& Zhou, T. (2024). Multimodal Fake News Detection with Contrastive Learning and Optimal Transport. \textit{Frontiers in Computer Science, 6}. \url{https://doi.org/10.3389/fcomp.2024.1473457}

\bibitem{ref44}
Geirhos, R., Jacobsen, J., Michaelis, C., Zemel, R., Brendel, W., Bethge, M., \& Wichmann, F. A. (2020). Shortcut learning in deep neural networks. \textit{Nature Machine Intelligence, 2}(11), 665--673. \url{https://doi.org/10.1038/s42256-020-00257-z}

\bibitem{ref45}
Understanding Model Calibration - A gentle introduction and visual exploration of calibration and the expected calibration error (ECE). (n.d.). \url{https://arxiv.org/html/2501.19047v2}

\bibitem{ref46}
KGALIGN: Joint Semantic-Structural Knowledge Encoding for Multimodal Fake news Detection. (n.d.). \url{https://arxiv.org/html/2505.14714v1}

\bibitem{ref47}
Zhang, L., Zhang, X., Zhou, Z., Zhang, X., Yu, P. S., \& Li, C. (2025). Knowledge-aware multimodal pre-training for fake news detection. \textit{Information Fusion, 114}, 102693. \url{https://www.sciencedirect.com/science/article/abs/pii/S1566253524004937}

\bibitem{ref48}
Alqadi, B. S., Alsuhibany, S. A., Yousafzai, S. N., Alzu'bi, S., Alsekait, D. M., \& AbdElminaam, D. S. (2025). Transfer learning driven fake news detection and classification using large language models. \textit{Scientific Reports, 15}(1), 28490. \url{https://doi.org/10.1038/s41598-025-10670-2}

\bibitem{ref49}
Wu, J., \& Zhang, Y. (2025, December 14). Imbalanced Fake News Detection Method Based on Multi-modal Adaptive Fusion. In \textit{Proceedings of the International Conference ACM}. \url{https://doi.org/10.1145/3796731.3796810}

\end{thebibliography}
\endgroup